A Case Study in Preserving a\\High Energy Physics Application

### 2014-03-19 paper.tex
Edited sections 4 and 5.

The overall reproduction of a computation has three broad components,
each of which suggests somewhat different approaches:

@@

In a very abstract sense, reproducing a computation is trivial.
Assuming a computation is deterministic, one must simply
preserve all of the inputs to a computation, then re-run
the same code in an equivalent environment, and the same result
will be produced.  For a small custom application on a modest
amount of data, this could be accomplished by capturing the environment,
data, and software within a single virtual machine image,
and then depositing the virtual
it into a curated environment.  The publication could
then simply refer to the identifier of the image, which the
interested reader can obtain and re-use. This approach has
been used to some success with systems mentioned in~\cite{castagne2013consider}.
\footnote{Of course, we are glossing over the problem that hardware
architectures and virtual machines also change, so one must also
preserve the VMM software necessary to run the image.  The VMM itself
depends on a software environment which must also be preserved.
A long-term preservation system might end up running a whole
stack of nested virtual machines in order to provide the desired
environment! }

@@

\begin{itemize}
\item There may be {\bf implicit dependencies} on items that are
not apparent to the end user.  For example, they may understand that
they rely on a particular data analysis package, but would have
no reason to know that the package has further dependencies on
other libraries and configuration files.  Or, they may know that
the computation only runs correctly on a particular machine, but
not know this is because it relies on data in a filesystem that
is mounted only on that machine.

@@

We do not claim to have solved these problems in any comprehensive
way.  Rather, our aim in this paper is to highlight the scope
of the problems by presenting a case study of one complex application.
The application is presented to us
first in the form of an email that describes in prose how to install
the software and run the analysis.  We perform several successive
refinements to convert it into an executable and preservable object.
Then, we develop two techniques for observing and capturing the
dependencies associated with the system, comparing the cost of capture,
the size of the preserved object, and the flexibility of the resulting
object.  
We propose one fine-grained dependency management toolkit to preserve the application and demonstrate its correctness in two different environments - one virtual machine from Notre Dame Cloud Platform and one virtual machine from Amazon EC2 Platform. 
We describe how each of these techniques may interact with
a future archive of preserved software artifacts, and conclude with
some reflections on the challenges of preservation and advice for future efforts.

@@

\section{Overview of Tau Analysis}

@@

Figure~\ref{fig:data-code-size} shows that both the code and data
that form \emph{TauRoast} are drawn from large repositories through
multiple steps of reduction.

@@

As AOD data are too large to be iteratively processed repetitively in
an physics analysis workflow, it is normally reduced further in
structural complexity and content.  For the analysis under
investigation here, this is a two-step process.  First, the AOD data
are processed at the Notre Dame working group cluster to BEAN events,
containing only trivial data containers packed in vectors.  This step
is time and CPU intensive and its output contains data of 11.6$\,$TB to be
analyzed by the tau analysis.
It is performed by a small custom code framework,
which is built on top of the CMS software stack, CMSSW~\cite{cms2006cmssw},
and uses packages provided by several other special interest groups within CMS.
While the CMSSW framework is installed locally,
the various packages used are checked out from CVS,
and the BEAN framework is stored in git.
This is scheduled to change,
as the CMSSW distribution model switches to a virtual filesystem mounted via FUSE,
and special interest groups move their code to git.
The BEAN format, production code, and
data are shared within the analysis group looking at Higgs production
in association with top quarks, which is formed by groups from a few
American and European universities,
consisting of up to a few dozen contributors.

In the second step, which is the beginning of the actual tau analysis,
the data are reduced to variables relevant to the tau roast procedure, while
only events matching basic quality criteria are kept.  This results in
a dataset of 43.3$\,$GB.  Again, the Notre Dame CMS groups cluster
resources are used to perform this reduction and selection,
running highly customized software,
built on CMSSW and the BEAN framework,
but with output code written and maintained by a few people only.
Again, the code is stored in a git repository.

The final data analysis, investigated below, can be run as a single
process, and contains a stringent event selection to keep only high
quality candidate events for the underlying physical process (using
about 20$\,$MB of space).  Quantities from the selected events can be
both plotted and used in multivariate analysis to determine the level
of expected signal in real data.
This package is written using the CMSSW build framework,
but only utilizes code from ROOT,
a particle physics toolkit underlying CMSSW,
and a few external python dependencies for convenience.
The latter have to be manually fetched and installed,
while the analysis program is built by CMSSW after being checked out of git.

The largest of these repositories is the CMS Software Distribution (CMSSW),
a carefully-curated selection of software packages which is distributed
in several forms.  Historically, components of CMSSW were obtained by checking components
of the source out of CVS, or by installing a complete binary package on a shared
filesystem within an HPC center.  In recent years, distribution has moved to
an on-demand delivery system known as CVMFS~\cite{blomer2011cernvm}.  The content
of CMSSW is managed very carefully by a centralized team whose main goal
is to ensure that the current version of the software operates correctly
on the operating systems and architectures currently in use.  However,
preservation is not an objective of the group, and so there is
no guarantee that old versions of CMSSW operate in new environments,
or vice versa.

@@

It is clear that the artifact, as provided, is not in a suitable form
for preservation.  While it might be technically possible to automatically
capture the entire virtual machine and all of the connected filesystems,
doing so would be wasteful and prohibitively expensive.  Further, if multiple
similar applications are preserved, we would miss the opportunity to identify
common dependencies and store them once for multiple artifacts.

Figure~\ref{fig:version-evolution} shows how we have evolved this artifact
through several stages which make it more suitable for preservation.
In each step of evolution, we make the dependencies of the artifact
more explicit and available for analysis and automated processing.
As noted in the previous section, the original author provided us with
prose instructions by email which we translated into an
executable script.  The executable script has embedded in it
a number of external identifiers such as URLs pointing to repositories
and paths to networked filesystems.  As a general programming practice,
embedding such constants into the middle of a program is unwise, and so
we extract all of those identifiers and place them at the beginning
of the script in the form of variable substitutions.  This makes
it readily apparent to the reader what the dependencies are.

Form 4 goes a step further and takes all of the dependencies \emph{out}
of the script itself and places them in a \emph{dependency map}.
The dependency map lists all of the external dependencies of the application, indicating
the type, how they are accessed, and where they are currently located.
The resulting script then simply refers to abstract file locations such
as \verb!$CMSSW!, while the map file indicates where they are located.
If properly constructed, the script should not refer to any external
resource unless it is indicated in the dependency map.

By extracting the dependencies into the external dependency map,
we introduce great freedom for the curator to move, transform, and otherwise
manipulate the dependencies of the artifact without damaging the artifact itself.
For example, it is straightforward for an automated tool to examine
all of the dependencies in the map, download those that are missing,
and then modify the map to point to the local copies of the dependencies.
(Or, in the case of a dependency upon a reliable external archive,
the map file could continue to point to the original source.)

\section{Fine Grained Dependency Management}

The difficulty of data access authority acquisition enforces us to find out one
solution, in which the reproduction of the original analysis can be done
without any external dependency. One independent and self-contained
package containing all the data and software dependencies is necessary. 
Two questions must be answered for this aim.

{\bf First, who should be responsible to generate the package?}
Someone may suggest that it should be the responsibility of the original author
to generate the required package. However, letting the original author provide
the package is unrealistic. 
Figuring out the underlying dependencies of
each software is complex and time-consuming and even impossible for the
original author. In this application, the machine used for the application is one
public machine of physics department, and the original author is one common user without
root authority. The underlying OS and supporting softwares are installed and
maintained by the IT department of the university. On the other hand, the
architecture design of the required package including all the data and software
dependencies is not under the research field of physicists.
Therefore, one packaging utility is necessary to help the original author to generate the package.

{\bf Second, how to figure out the implicit dependencies?}
With the help of the formulated script, we can easily figure out the explicit dependencies.
The requirements of the underlying OS and hardware
architecture can be easily found with system tools such as {\tt uname} or
{\tt lsb\_release}.
However, how to figure out the implicit dependencies needs more concerns, because
directly preserving the whole OS together with the data
stored on the disk of the original machine or the data from other filesystems
mounted as local filesystems, such as HDFS and PanFS, is not feasible. One
efficient mechanism which can figure out the really used parts of all these
filesystems is necessary. 
To do this, the file access details of the application should be tracked and utilized.

@@

When we try to repeat one application on one new machine, one map file is necessary for the relocation of the data access targets, as
show in Figure~\ref{fig:version-evolution}. 
The map file clearly defines the real location of each dependency in the format of dependency variables - the real location of dependency variable {\tt GIT} is \path{http://github.com} and the real location of dependency variable {\tt CVMFS}
is {\tt /tmp/package-hep/cvmfs}.
The script only refers to the dependency variables defined in the map file.
This design decouples the application script and the actual data access targets, which minimizes the impact of the evolution of different data dependencies
and ensures the transparent access.
The modification of the package only introduces the minimal changes of the map file on the client side.

\section{One Fine Grained Dependency Management Toolkit Based on Parrot}

@@

With the help of one
virtual filesystem access tool, Parrot~\cite{thain2005parrot}, we trap all system calls of one
program through ptrace debugging interface, and collect all the names of accessed files. 
Then one self-contained package containing all the accessed files is generated to help others repeat the application.

Parrot is a virtual filesystem access tool which attaching existing programs to
a variety of remote {\tt I/O} systems including 
HTTP, FTP, GridFTP, iRODS, HDFS, XRootD, GROW, and Chirp. It traps all system calls of one program through ptrace
debugging interface, and replaces them with remote {\tt I/O} operations as desired.

Figure~\ref{fig:workflow-parrot} illustrates the workflow of the fine-grained dependency management toolkit based on Parrot.
The starting point of this toolkit is one successful execution of the application on the native machine.
First, re-execute the actual
data analysis script under Parrot and get the name list of all the files actually
accessed during the data analysis process. Then,
according to the filename list, one package containing all the necessary data
and software for one analysis program is generated. When another
scholar wants to repeat the program, he only needs to obtain the package and
execute the actual analysis program inside the package.

The filename list contains the names of 132,047 accessed file, together with the access type of each file, such as
open, stat, read and write. 
We noticed that some files appeared multiple times in the filename list. 
De-duplication and sorting techniques are used to deal with the original filename list, generating one smaller list containing 67,168 items.
The total size of each involved directory and file is 900.3GB.

The toolkit iterates each item of the filename list, determines the process
mode and replication degree according to the file type (common files,
directories, symbolic links) and the system call type, generates one package
containing all the necessary file dependencies, and returns the description
information of the package, as shown in Table~\ref{table:package-info}.  To
ensure the successful reproduction, the filesystem structure of the original
execution environment should be preserved as completely as possible. However,
attempting to copy the whole content of one directory or one file is
space-consuming and time-consuming, because the original program may 
only need to know how many items one directory contains and not need the content of the sub-directories or the sub-files.
Our solution is to
determine the replication degree of one directory or one file according to the
system call type. 
If one file is accessed through system calls like {\tt open}, {\tt read} and {\tt write}, the whole content of the file will be copied into the package.
However, if the application only needs to check the existence of one file through {\tt stat} system call, we only create an empty file in the package.
As for a directory item, the sub-items under it will be copied into the package if their contents are necessary. Otherwise, we only create empty sub-items in the package to maintain the directory structure.
The step also runs under Parrot to access data from
different file systems.

\begin{table}
    \centering
    \begin{tabular}{|l|}
    \hline
     the total size of package: 21GB \\ 
    the total number of files: 15905\\ 
    the total number of directory: 1549\\ 
    the total number of symbolic link: 4614 \\ \hline 
    \end{tabular}
    \caption{Package Information}
    \label{table:package-info}
\end{table}

The package, the Parrot executable program, together with the environment description information of the application, such as hardware platform, OS version and kernel version, will be published.

When another researcher wants to repeat the analysis program,
one map file, which maintains the relationship between the file access path referred in the program of the application and the actual file location 
, will be generated, as shown in Table~\ref{table:map-file}.
The path of the package is {\tt /tmp/package-hep}, so the actual location of one file with the original path {\tt path1} will be {\tt /tmp/package-hep/path1}.
However, 
it is impossible to copy the files under certain directories, such as  {\tt /dev}, which contains all the device files.
Each device file is either a block file or a character file. 
The new machine may not share the same device configuration with the original machine, so copying block files into the package is meaningless.
Copying character files such as /dev/tty and /dev/urandom is also meaningless because of their dynamic nature.
It is meaningless to copy the file under the directory {\tt /proc}, 
because OS may allocate different process IDs for multiple executions of one application.
As for these special file paths, letting
the program directly utilize the files on the new machine, where the new user
repeats the program, is a better choice. 
The item {\tt /dev /dev} of Table~\ref{table:map-file}
illustrates this semantics.
With the help of the map file and the package, the application can be repeated on one new machine.

@@

\section{Evaluation}
We evaluated the correctness and overhead of the packaging utility of Solution 4.
To do it, the application was repeated using Solution 2 and 4 on the original machine.
Then, two different virtual machines (VM) - one VM from Notre Dame Cloud Platform based on KVM and one VM from Amazon EC2 Platform based on Xen, were employed to further verify the correctness of Solution 4.

@@

\begin{table}
    \centering
    \begin{tabular}{|l|r|r|}
    \hline
    \bf Task & \bf Solution 2& \bf Solution 4\\ 
    \bf Category & \bf Time & \bf Time \\ \hline
    Obtain filename list & N/A & 28min 28s \\ \hline
    Generate package & N/A & 85min 51s \\ \hline
    Software Acquisition & 8min 11s & N/A \\ \hline
    Environment Build & 5min 49s  & 4s \\ \hline
    Actual Analysis & 20min 31s & 13min 04s \\ \hline
    \end{tabular}
    \caption{Execution Time Comparison between Solution 2 and 4}
    \label{table:time-2nd3rd}
\end{table}

>>>>

The reproduction of a computation has three broad components,
each of which suggests somewhat different approaches:

@@

In a very abstract sense, reproducing a computation is trivial.
Assuming a computation is deterministic, one must simply
preserve all of the inputs to a computation, then re-run
the same code in an equivalent environment, and the same result
will be produced.  For a small custom application on a modest
amount of data, this could be accomplished by capturing the
complete environment,
data, and software within a single virtual machine image,
and then depositing the virtual
it into a curated environment.  The publication could
then simply refer to the identifier of the image, which the
interested reader can obtain and re-use. This approach has
been used to some success with systems mentioned in~\cite{castagne2013consider}.
\footnote{Of course, we are glossing over the problem that hardware
architectures and virtual machines also change, so one must also
preserve the VMM software necessary to run the image.  The VMM itself
depends on a software environment which must also be preserved.
A long-term preservation system might end up running a whole
stack of nested virtual machines in order to provide the desired
environment! }

@@

\begin{itemize}
\item There may be {\bf implicit dependencies} on items that are
not apparent to the end user.  For example, they may understand that
they rely on a particular data analysis package, but would have
no reason to know that the package has further dependencies on
other libraries and configuration files.  Or, they may know that
the computation only runs correctly on a particular machine, but
not know this is because it relies on a filesystem that
is mounted only on that machine.

@@

We do not claim to have solved these problems in any comprehensive
way.  Rather, our aim in this paper is to highlight the scope
of the problems by presenting a case study of one complex application.
The application is presented to us
first in the form of an email that describes in prose how to install
the software and run the analysis.  We perform several successive
refinements to convert it into an executable and preservable object.
We then develop techniques for reducing the size of the dependencies
that are necessary for the object to function, and we demonstrate
the preserved object functioning correctly in three different
physical and cloud environments.
We describe how each of these techniques may interact with
a future archive of preserved software artifacts, and conclude with
some reflections on the challenges of preservation and advice for future efforts.

@@

\section{Overview of Tau Roast}

@@

Figure~\ref{fig:data-code-size} shows that both the code and data
that form \emph{TauRoast} are drawn from large repositories through
multiple steps of reduction.  A preservation strategy must weigh
whether to store the large repositories completely, the fragments
used by an artifact, or something in between.

The largest of these repositories is the CMS Software Distribution (CMSSW),
a carefully-curated selection of software packages which is distributed
in several forms.  Historically, components of CMSSW were obtained by checking components
of the source out of CVS, or by installing a complete binary package on a shared
filesystem within an HPC center.  In recent years, distribution has moved to
an on-demand delivery system known as CVMFS~\cite{blomer2011cernvm}, which
provides a filesystem interface that transparently accesses a remote repository.
The content of CMSSW is managed very carefully by a centralized team whose main goal
is to ensure that the current version of the software operates correctly
on the operating systems and architectures currently in use.  However,
preservation is not a specific objective of the system, and so there is
no particular guarantee that old versions of CMSSW will continue to
operate indefinitely.

CMSSW contains many different tools, libraries, and utilities.  No single code uses anywhere close to all of that.  But, because it is widely used within the community, it is common for users and developers to simply expect that a particular version of the entire repository is available.

@@

As AOD data are too large to be iteratively processed repetitively in
an physics analysis workflow, it is normally reduced further in
structural complexity and content.  For the analysis under
investigation here, this is a two-step process.  First, the AOD data
are processed at the Notre Dame working group cluster to BEAN events,
containing only trivial data containers packed in vectors.  This step
is time and CPU intensive and its output contains data of 11.6$\,$TB to be
analyzed by the tau analysis.
It is performed by a small custom code framework, which is built on top of CMSSW.
The BEAN format, production code, and
data are shared within the analysis group looking at Higgs production
in association with top quarks, which is formed by groups from a few
American and European universities,
consisting of up to a few dozen contributors.

In the second step, the data are reduced to the ``Ntuple'' format,
which contains only events matching basic quality criteria and
fields relevant to \emph{TauRoast}. This results in
a dataset of 43.3$\,$GB.  Again, the Notre Dame CMS groups cluster
resources are used to perform this reduction and selection,
running highly customized software,
built on CMSSW and the BEAN framework,
with code written and maintained by a small group.

Once the data has been reduced to Ntuples, TauRoast can be run as a single
process, and contains a stringent event selection to keep only high
quality candidate events for the underlying physical process (using
about 20$\,$MB of space).  Quantities from the selected events can be
both plotted and used in multivariate analysis to determine the level
of expected signal in real data.
This package is written using the CMSSW build framework,
but only utilizes code from ROOT,
a particle physics toolkit underlying CMSSW,
and a few external python dependencies for convenience.

@@

It is clear that the artifact, as provided, is not in a suitable form
for preservation.  While it might be technically possible to automatically
capture the entire virtual machine and all of the connected filesystems,
it would require 166.8TB of storage, which would be prohibitively expensive
for capturing this one application is alone.  Further, if multiple
similar applications are preserved, we would miss the opportunity to identify
common dependencies and store them once for multiple artifacts.
A more structured approach to dependency management is needed.

Figure~\ref{fig:version-evolution} shows how we have evolved this artifact
through several stages which make it more suitable for preservation.
In each step of evolution, we make the dependencies of the artifact
more explicit and available for analysis and automated processing.
As noted in the previous section, the original author provided us with
prose instructions by email which we translated into an
executable script.  The executable script has embedded in it
a number of external identifiers such as URLs pointing to repositories
and paths to networked filesystems.  As a general programming practice,
embedding such constants into the middle of a program is unwise, and so
we extract all of those identifiers and place them \emph{outside} the
script in a \emph{dependency map} or just \emph{map} for short.
The dependency map lists all of the external dependencies of the application, indicating
the type, how they are accessed, and where they are currently located.
The resulting script then simply refers to abstract file locations such
as \verb$GIT$ and \verb!$CMSSW!, while the map file indicates where they
are currently located. If properly constructed, the script should not refer to any external
resource unless it is indicated in the dependency map.  We call this idealized
artifact an \emph{abstract script}.

By extracting the dependencies into the dependency map,
we introduce great freedom for the curator to move, transform, and otherwise
manipulate the dependencies of the artifact without damaging the artifact itself.
A Figure~\ref{fig:version-evolution} shows, it is straightforward for an
automated tool to examine
all of the dependencies in the map, download those that are missing,
and then modify the map to point to the local copies of the dependencies.
If we group the script, dependency map, and dependencies into a \emph{package},
we now have a self-contained artifact that can be moved from place to place.
In some cases, it may be safe to allow the dependency map to refer to 
trusted remote repositories.  Whether this is advisable is a judgement that
must be made by the user or the curator, taking into account the long-term
stability of said repositories.

@@

When we try to repeat one application on one new machine, one map file is necessary for the relocation of the data access targets, as
show in Figure~\ref{fig:version-evolution}. 
The map file clearly defines the real location of each dependency in the format of dependency variables - the real location of dependency variable {\tt GIT} is \path{http://github.com} and the real location of dependency variable {\tt CVMFS}
is {\tt /tmp/package-hep/cvmfs}.
The script only refers to the dependency variables defined in the map file.
This design decouples the application script and the actual data access targets, which minimizes the impact of the evolution of different data dependencies
and ensures the transparent access.
he modification of the package only introduces the minimal changes of the map file on the client side.

This basic approach to dependency management is a step in the right direction
for dependencies that are \emph{explicit} and \emph{external} to the
user's native execution environment.  However, it leaves two other problems unsolved.

First, the basic approach requires that someone be \emph{aware} of the dependencies,
whether it be the end user, the system administrator, or the archive curator.
It seems reasonable to expect the user to be aware of a large dependency mentioned in a top-level script.
But, oftentimes the dependency is embedded invisibly deep within the software stack,
or is connected to the machine by the local system administrators.  No single party
is likely to have complete information about all of the dependencies.
Second, the basic approach assumes that the entire dependency is actually
consumed by the artifact.  As we have suggested above (and will show below),
this sort of program often only consumes a small fraction of what it does declare
as a dependency.

To address both of these problems, users and curators alike need tools that
will automatically observe the dependencies of complex applications, to
facilitate automatic and efficient preservation.

\section{Measuring Dependencies}

@@

We have developed a prototype tool to assist in the measurement and preservation
of implicit dependencies for complex applications.
We use Parrot~\cite{thain2005parrot} to explicitly record all
of the files accessed by our example application, allowing us to observe how
much of each external dependencies is used, and what local resources are implicitly used.
Using this information, we create a \emph{reduced package} which contains
only the files actually used by the application.

Parrot is a virtual filesystem access tool which has previously been used to attach
exisiting programs to a variety of remote I/O systems, such as HTTP, FTP, and CVMFS.
It works by trapping an application's system calls through the {\tt ptrace} debugging
interface, and then replacing them with the desired I/O operations.  Parrot is already used
in the high energy physics community with applications like TauRoast specifically to 
provide access to the CMSSW software distribution via the CVMFS distributed file system.
We made small modifications to Parrot to record a \emph{namelist} which lists all 
of the files that an application actually accesses.

Figure~\ref{fig:workflow-parrot} illustrates the measurement process.
The starting point of this toolkit is one successful execution of the application on the native machine.
First, we execute the actual data analysis script under Parrot to generate the namelist.
Then, using the namelist, we generate a package containing all the necessary data
and software for one analysis program is generated. When another
researcher wants to repeat the program, he only needs to obtain the package and
execute the actual analysis program inside the package.

For one execution of \emph{TauRoast}, the namelist 132,047 accessed filenames,
along with the operation used to access the file, such as {\tt open}, {\tt stat}, {\tt read}, etc.
With duplicate filenames removed, the list is reduced to 67,168 files.
Many of those entries do not exist, because they reflect attempts
by the application to search for programs and libraries in multiple places.
Only 22,068 entries reflect existing files or directories.

The packaging tool iterates over each item of the filename list, determines the process
mode and replication degree according to the file type (common files,
directories, symbolic links) and the system call type, generates one package
containing the dependencies, and summarizes the contents of the package
as shown in Table~\ref{table:package-info}.  To the extent possible,
the filesystem structure of the original environment is preserved.

We considered several approaches to constructing the package.
In a {\bf shallow copy}, we only copied the individual files in the namelist,
creating only parent directories for each.  Where a directory was listed,
we created the directory and populated it with empty files as placeholders
to facilitate a directory listing.  In a {\bf medium copy}, we copied the
individual files as before.  Where a directory was listed, we created
the directories and copied the contents of the files in that directory,
one level deep.  A {\bf deep copy} would duplicate all directories recursively,
but this would have resulted in TB-sized packages, so we did not consider
it further.

Parrot is required to re-run the packaged artifact, in order to force
the packaged files to appear to exist in their original locations.
To this end, the packaging tool creates a \emph{file map} which maps
the logical names of the files to their current physical locations, as shown in Table~\ref{table:map-file}.
Parrot reads the file map and redirects system calls at run-time to achieve the desired effect.
As the example suggests, special device files such as {\tt /proc} and {\tt /dev}
are not incorporated into the package but are instead accessed natively.

@@

\begin{table}
    \centering
    \begin{tabular}{|r|r|r|}
\hline
                    & \bf Shallow Copy & \bf Medium Copy\\
\hline
    Whole Files:    & 1632         & 15642\\ 
\hline
    Empty Files:    & 14273        & 263\\
\hline
    Directories:    & 1549         & 1549\\ 
\hline
    Symbolic Links: & 4614         & ??? \\
\hline
    \bf Total Size: & \bf 21GB     & \bf 28GB \\ 
\hline
    \end{tabular}
    \caption{Package Information}
    \label{table:package-info}
\end{table}

\section{Evaluation}

We evaluated the correctness and overhead of the packaging utility of Solution 4.
To do it, the application was repeated using Solution 2 and 4 on the original machine.
Then, two different virtual machines (VM) - one VM from Notre Dame Cloud Platform based on KVM and one VM from Amazon EC2 Platform based on Xen, were employed to further verify the correctness of Solution 4.

@@

\begin{table}
    \centering
    \begin{tabular}{|l|r|r|}
    \hline
    \bf Task & \bf Original& \bf Reduced\\ 
    \bf Category & \bf Script & \bf Package\\ \hline
    Obtain Namelist & N/A & 28min 28s \\ \hline
    Generate Package & N/A & 85min 51s \\ \hline
    Software Acquisition & 8min 11s & N/A \\ \hline
    Environment Build & 5min 49s  & 4s \\ \hline
    Analysis Code & 20min 31s & 13min 04s \\ \hline
    \end{tabular}
    \caption{Execution Time Comparison between Solution 2 and 4}
    \label{table:time-2nd3rd}
\end{table}
